### 2017-09-28 TF-vldb2018/sec-intro.tex

This motivates us to study the {\em dynamic top-k team formation} problem (\dynteamF), to handle continuous 
pattern and data updates, separately and simultaneously.
As a basis of \dynteamF, we also investigate the incremental problem for graph pattern queries on pattern updates. 
The definition can be formulated along the same lines with the existing data incremental problem.
%different with data incremental algorithms that preserve some desirable properties that the recomputation can be {\em bounded}  by the changes in the input and output as the impact of data updates can be localized~\cite{Reps96, FanLMTWW10,FanWW13-tods,FanHT17}, 
However, devising pattern incremental algorithms is quite challenging as the impact of pattern updates is global,
due to the inherent hardness of the problem.
Despite of this, we devise an effective unified incremental approach for the \dynteamF\, problem.

>>>>

This motivates us to study the {\em dynamic top-k team formation} problem (\dynteamF), to handle continuous 
pattern and data updates, separately and simultaneously.
As a basis of \dynteamF, we also investigate the incremental problem for graph pattern matching on pattern updates. 
The definition can be formulated along the same line with existing data incremental problems.
%different with data incremental algorithms that preserve some desirable properties that the recomputation can be {\em bounded}  by the changes in the input and output as the impact of data updates can be localized~\cite{Reps96, FanLMTWW10,FanWW13-tods,FanHT17}, 
However, devising pattern incremental algorithms is quite challenging as the impact of pattern updates is global,
due to the inherent hardness of the problem.
Despite of this, we devise an effective unified incremental approach for the \dynteamF\, problem.
